### 2023-04-14 README.Rmd
Update README and FAQ vignette with info about Apptainer/Singularity

>>>>

### Using Apptainer/Singularity containers for HPC

A `rang` object can be used to recreate the computational environment via [Rocker](https://github.com/rocker-org/rocker). Instead of Docker you can also use [Apptainer/Singularity](https://apptainer.org/). Please note that the oldest R version one can get from Rocker is R 3.1.0.

```r
apptainerize(graph, "~/rocker_test")
# singularize(graph, "~/rocker_test") # same function, as so far Apptainer is identical to Singularity
```

Now, you can build and run the Apptainer/Singularity container.

For Apptainer installation:

```bash
cd ~/rocker_test
sudo apptainer build container.sif container.def
apptainer instance start container.sif rangtest
```

For Singularity installation:

```bash
cd ~/rocker_test
sudo singularity build container.sif container.def
singularity exec container.sif R
```

Using the above example, `sessionInfo()` outputs the following. You have successfully gone back to the pre-pandemic time on your HPC.

```
R version 3.6.2 (2019-12-12) -- "Dark and Stormy Night"
Copyright (C) 2019 The R Foundation for Statistical Computing
Platform: x86_64-pc-linux-gnu (64-bit)

R is free software and comes with ABSOLUTELY NO WARRANTY.
You are welcome to redistribute it under certain conditions.
Type 'license()' or 'licence()' for distribution details.

R is a collaborative project with many contributors.
Type 'contributors()' for more information and
'citation()' on how to cite R or R packages in publications.

Type 'demo()' for some demos, 'help()' for on-line help, or
'help.start()' for an HTML browser interface to help.
Type 'q()' to quit R.

> sessionInfo()
R version 3.6.2 (2019-12-12)
Platform: x86_64-pc-linux-gnu (64-bit)
Running under: Debian GNU/Linux 10 (buster)

locale:
 [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C
 [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8
 [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=C
 [7] LC_PAPER=en_US.UTF-8       LC_NAME=C
 [9] LC_ADDRESS=C               LC_TELEPHONE=C
[11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C

loaded via a namespace (and not attached):
[1] compiler_3.6.2
```

`apptainerize()`/`singularize()` functions work exactly the same as `dockerize()`, expect you cannot cache Linux distribution rootfs.
